\documentclass[a4paper, 11pt]{article}

% 日本語対応
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx} % 図の挿入
\usepackage[hidelinks]{hyperref} % リンク（枠・色を非表示）
\usepackage{url} % URL表示
\usepackage{enumitem} % リストのカスタマイズ
\usepackage{float} % 図表の配置制御

% 日本語環境の設定 (必要に応じて変更)
\usepackage[ipaex]{zxjafont} % XeLaTeX/LuaLaTeXの場合
% \usepackage[utf8]{inputenc} % pdfLaTeXの場合
% \usepackage[T1]{fontenc} % pdfLaTeXの場合
% \usepackage[japanese]{babel} % pdfLaTeXの場合

% タイトル、著者情報
\title{VOLE-in-the-Headゼロ知識証明のオンチェーン検証における実現可能性とコスト分析}
\author{著者名 \\ 所属機関}
\date{\today}

\begin{document}

\maketitle

\input{abstract.tex}

\newpage

% 各セクションの読み込み
\input{intro_background.tex}
\input{background.tex}
\input{benchmark_design.tex}
\input{results_analysis.tex}
\input{snark_insights.tex}
\input{related_work.tex}
\input{conclusion.tex}

\newpage
\section*{参考文献 (References)}
\begin{thebibliography}{99}
\bibitem{eprint:iacr:2023:681}
Iden3.
Circom: A Circuit Compiler for Zero-Knowledge Proofs.
\textit{Cryptology ePrint Archive}, Paper 2023/681, 2023.
\url{https://eprint.iacr.org/2023/681}.

\bibitem{eprint:2021:730}
Haitner, Y., et al.
Mystique: Efficient Conversions for Zero-Knowledge Proofs with Applications to Machine Learning.
\textit{Cryptology ePrint Archive}, Paper 2021/730, 2021.
\url{https://eprint.iacr.org/2021/730}.

\bibitem{eprint:2025:507}
Fu, H., et al.
Scalable Zero-knowledge Proofs for Non-linear Functions in Machine Learning.
\textit{Cryptology ePrint Archive}, Paper 2025/507, 2025.
\url{https://eprint.iacr.org/2025/507}.

\bibitem{eprint:2024:490}
Beullens, W., et al.
One Tree to Rule Them All: Optimizing GGM Trees and OWFs for Post-Quantum Signatures.
\textit{Cryptology ePrint Archive}, Paper 2024/490, 2024.
\url{https://eprint.iacr.org/2024/490}.
\end{thebibliography}

\end{document}
