\section*{参考文献 (References)}
\begin{thebibliography}{99}
\bibitem{voleith}
Baum, C., et al.
Publicly Verifiable Zero-Knowledge and Post-Quantum Signatures from VOLE-in-the-Head.
\textit{Cryptology ePrint Archive}, Paper 2023/996, 2023.
\url{https://eprint.iacr.org/2023/996}.

\bibitem{groth16}
Groth, J.
On the Size of Pairing-based Noninteractive Arguments.
In \textit{EUROCRYPT 2016}, pp. 305-326, 2016.
DOI: \url{10.1007/978-3-662-49896-5_11}.

\bibitem{plonk}
Gabizon, A., Williamson, Z. J., and Ciobotaru, O.
PLONK: Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge.
\textit{IACR Cryptology ePrint Archive}, 2019.

\bibitem{poseidon}
Grassi, L., et al.
Poseidon: A New Hash Function for Zero-Knowledge Proof Systems.
In \textit{USENIX Security Symposium}, 2021.
\url{https://www.usenix.org/conference/usenixsecurity21/presentation/grassi}.

\bibitem{eprint:iacr:2023:681}
Iden3.
Circom: A Circuit Compiler for Zero-Knowledge Proofs.
\textit{Cryptology ePrint Archive}, Paper 2023/681, 2023.
\url{https://eprint.iacr.org/2023/681}.

\bibitem{eprint:2021:730}
Haitner, Y., et al.
Mystique: Efficient Conversions for Zero-Knowledge Proofs with Applications to Machine Learning.
\textit{Cryptology ePrint Archive}, Paper 2021/730, 2021.
\url{https://eprint.iacr.org/2021/730}.

\bibitem{eprint:2025:507}
Fu, H., et al.
Scalable Zero-knowledge Proofs for Non-linear Functions in Machine Learning.
\textit{Cryptology ePrint Archive}, Paper 2025/507, 2025.
\url{https://eprint.iacr.org/2025/507}.

\bibitem{eprint:2024:490}
Beullens, W., et al.
One Tree to Rule Them All: Optimizing GGM Trees and OWFs for Post-Quantum Signatures.
\textit{Cryptology ePrint Archive}, Paper 2024/490, 2024.
\url{https://eprint.iacr.org/2024/490}.

\bibitem{quicksilver}
Yang, K., Kohl, P., and Song, D.
QuickSilver: Efficient and Affordable Zero-Knowledge Proofs for Circuits and Polynomials.
In \textit{Proceedings of the ACM SIGSAC Conference on Computer and Communications Security (CCS '21)}, pp. 233-250, 2021.
DOI: \url{10.1145/3460120.3484550}.

\bibitem{fiatshamir}
Fiat, A., and Shamir, A.
How to Prove Yourself: Practical Solutions to Identification and Signature Problems.
In \textit{Advances in Cryptology -- CRYPTO '86}, pp. 186-194, 1987.
DOI: \url{10.1007/3-540-47721-7_12}.

\bibitem{yellowpaper}
Wood, G.
Ethereum: A Secure Decentralised Generalized Transaction Ledger.
\textit{Ethereum Project Yellow Paper}, 2024.
\url{https://ethereum.github.io/yellowpaper/paper.pdf}.
\end{thebibliography}
